\documentclass[xcolor=dvipsnames,hyperref={pdfpagelabels=false}]{beamer}

\usetheme{Boadilla}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\I}{\item}
\newcommand{\f}{\frame}
\newcommand{\ft}{\frametitle}

\title{Offline Software Overview}
\subtitle{GlueX Collaboration Meeting}
\author[Mark Ito]{Mark M.\ Ito}
\date{May 13, 2014}
\institute[JLab]{Jefferson Lab}

\begin{document}

\f{\titlepage}

\f{\ft{Outline}
\bi
\I Data Challenge
  \bi
  \I goals
  \I conditions
  \I sites
  \I organization
  \I issues
  \I results
  \I next
  \I outcomes
  \ei
\I Other Topics
\I To Do
\ei
}

\end{document}

outline
data challenge
  goals
    include curtis's slide:  February  2014 Data Challenge
    Nominal goal is 10 billion events.
    Phythia/BGGEN events from 7.0GeV to the endpoint.
    Normal run will be in REST format.
    Specialized block (at JLab) that retains HDGEANT output (for tape tests)?
    Target distribution to be nominal LH2 as handled by HDGEANT.
    1350 magnetic field
    updated REST format, matching info saved
    use the CCDB
  conditions
    versions
    background settings
    file number assignments
  sites
    jlab
      workflow tools at JLab not ready
    mit
      OpenStack at MIT
      futuregrid
        futuregrid at 180 cores (3/28)
        MIT 300 cores with futuregrid
    cmu
    fsu
    osg
      UConn
      nw
  organization
    series of meetings held in addition to the offline software meeting
      curtis initiated
    conditions page
    event tally board
  issues
    Reversed magnetic field fixes from Simon
    effect of EM background on file size and execution time
      Kei study, varied gate widths as well
    phi = 0 problem in CDC solved
    event geneology checked
    A fix from Simon for single-ended TOF counters.
    Improvements from Paul for cutting off processing for multi-lap curling tracks. big memory footprint effect
    ZFATAL fix from richard, showers from EM background, squelched
    short rest, compression
       short rest file fix from richard: bug in xstream library with compression enabled
    non-reproducibility
       reproducibility fixed: sort needed on associated objects in STL map
    random number seeds
      looked at scheme where every event stores its seed at each stage
      settled on bggen seed
    Kei studies on em background for pπ+π- pπ+π-π0
    job tracking with farm at JLab info
    python script to scan monitoring histograms from Sean
  results
    code frozen on 3/20
    events produced
    execution time
      running times for various em bg conditions from Paul (3/7)
    memory usage
    reliability:
      CMU: 7000 jobs, 3 failures
      JLab: 69,000 jobs, about 30 failures
    node history
      farm nodes increase at JLab
        The current farm is at about 1200 cores. The farm typically 1400 cores. For the 25% level test we will need 1250 cores. The plan is to bring another 1000 cores over from LQCD to keep the farm generally usable.
        Lattice nodes are available to us because Physics has been lending 32 16-core nodes to the LQCD farm all of December and January.
        3400 cores now in farm, 2400 for Hall D (3/4)
        plot from Mark
        plot from Sandy
    ramp down April 11 plus or minus a few days, last data challenge meeting
  data distribution
    srm
      archiving all data to tape library
    event store
    paul: proposed skims
  next data challenge
    multi threading
    tape overhead
    needed: raw data, ability to analyze it
    time frame
  what came out
    em background
    usable data set
    large usable data set
    improvements of techniques at various sites
    collaborative efforts can succeed
    need for geant4
    monitoring system
      rootspy?
other topics
  CCDB 1.00 released
  kinematic fitter update
  paul: proposed skims
  database and webserver changes coming up
  nightly build using scons
  bluejeans deployed: Curtis
summary
  to do
    splitting up packages
    re-org of offline wiki pages

