\documentclass{beamer}

\usepackage{epsfig}
\usetheme{AnnArbor}

\title{Software Version Discussion}
\author[M.\ Ito]{Mark M.\ Ito}
\date{December 17, 2008}
\institute[JLab]{Jefferson Lab}

\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\benum}{\begin{enumerate}}
\newcommand{\eenum}{\end{enumerate}}
\newcommand{\bcent}{\begin{center}}
\newcommand{\ecent}{\end{center}}

\begin{document}

\frame{\titlepage}

\frame{
\frametitle{Standard Software Versions}
\bitem
\item All collaborations have them
\item Common language for problem solving
\item Reference for re-examining past work
\item Mundane building work can benefit others
\eitem
}

\frame{
\frametitle{Possible Standard Version Types}
\bitem
\item Nightly
\bitem
\item latest and greatest
\eitem
\item Development
\bitem
\item integration testing platform
\eitem
\item Weekly and/or Monthly
\bitem
\item semi-stable latest and greatest
\eitem
\item Production
\bitem
\item ``kept'' for life of experiment
\item standard naming convention
\eitem
\item Others?
\item Right now:
\bitem
\item Nightly
\item Bi-monthly/Production
\eitem
\eitem
}

\frame{
\frametitle{External package management}
\bitem
\item for example: root, cernlib, xerces, clhep, geant4, xalan, java, perl, mysql, gcc,...
\item want collaboration wide agreement
\item want efficient communication/distribution method (for internal packages too)
\item want not to discuss this today(?)
\eitem
}

\frame{
\frametitle{Possible Standard Platforms}
\bitem
\item Linux Fedora 8 (JLab farm)
\item Linux RedHat Enterprise 5 (JLab desktop)
\item Mac OSX (popular)
\item Linux Ubuntu (also popular)
\item SunOS/Solaris
\item etc.
\eitem
}

\frame{
\frametitle{Questions}
\bitem
\item What do we want?
\bitem
\item What versions?
\item What platforms?
\eitem
\item When do we want it?
\item Who is going to decide?
\item Who is going to do it?
\eitem
}

\end{document}

%%% end of latex file %%%%
