\documentclass[xcolor=dvipsnames,hyperref={pdfpagelabels=false}]{beamer}

\usetheme{Boadilla}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\I}{\item}
\newcommand{\f}{\frame}
\newcommand{\ft}{\frametitle}

\title{Version Management}
\subtitle{Status Report}
\author[Mark Ito]{Mark M.\ Ito}
\date{December 10, 2014}
\institute[JLab]{Jefferson Lab}

\begin{document}

\f{\titlepage}

\f{\ft{Use Cases}
\be
\I Communicate a consistent set of versions.
  \bi
  \I Identify working combinations
  \I Coordinate collaborative work
  \ei
\I Specify a set of versions to be built.
  \bi
  \I Green-field builds
  \I Adding versions to existing build trees
  \ei
\I Set-up environment to use specific versions.
  \bi
  \I Ensure consistency with desired set of versions.
  \ei
\ee
}

\begin{frame}[fragile]
\frametitle{XML configuration file}
\small
\begin{verbatim}
<gversions>
<package name="jana" version="0.7.2"/>
<package name="sim-recon" version="2014-09-23"/>
<package name="hdds" version="3.0"/>
<package name="cernlib" version="2005"/>
<package name="xerces-c" version="3.1.1"/>
<package name="clhep" version="2.0.4.5"/>
<package name="geant4" version="9.4"/>
<package name="root" version="5.34.04"/>
<package name="ccdb" version="1.03"/>
<package name="evio" version="4.3.1"/>
</gversions>
\end{verbatim}
\end{frame}

\f{
\ft{generate environment variables}
\bi
\I For each package generate two environment variables
  \be
  \I version number
  \I home directory
  \ee
\I C shell and Bourne shell supported
\I build\_scripts makefiles key off version
\I gluex\_install assumes same directory structure
\I gluex\_env (in build scripts) keys off home directories
\ei
}

\begin{frame}[fragile]
\ft{example environment settings}
\small
\begin{verbatim}
setenv GLUEX_TOP /usr/local/gluex;
setenv JANA_VERSION 0.7.2;
setenv JANA_HOME /usr/local/gluex/jana/jana_0.7.2/Linux_RHEL6-x86_64-gcc4.4.7;
setenv SIM_RECON_VERSION 2014-09-23;
setenv HALLD_HOME /usr/local/gluex/sim-recon/sim-recon-2014-09-23;
setenv HDDS_VERSION 3.0;
setenv HDDS_HOME /usr/local/gluex/hdds/hdds-3.0;
\end{verbatim}
\end{frame}

\f{
\ft{customization for non-standard directory structure}
\bi
\I if not using the same directory structure?
\I version-system home area definitions can be over-ridden explicitly
\I subsequent gluex\_env will respect those
\ei
}

\f{
\ft{future work}
\bi
\I follow ``prod'' links when checking consistency
\I version xml file management system
  \bi
  \I version numbers?
  \I subversion control?
  \I distribution system?
  \ei
\I scheme for concurrent versions of fixed package version built with different prerequisites
\I documentation
\ei
}

\end{document}
